### 2012-12-30 manuscript.tex
corrigi pequenos erros de ortigrafia

% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}
We would like to thank Claudia Torres Codeço, Paulo Cezar Carvalho and Moacyr silva for fruitful discussions and key ideas which helped improve the manuscript.

>>>>

% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}
We would like to thank Claudia Torres Code\c{c}o, Paulo Cezar Carvalho and Moacyr Silva for fruitful discussions and key ideas which helped improve the manuscript.
